### 2020-04-08 draft.tex

We will show that $\Dir_{/_{\ulcorner} D}$ is a subtopos of $\Dir_{/D}$ with the
lex localization (``inverse image functor'') given by the vertical / cartesian factorization system on $\Set^{\down}$.

\begin{thm}
  For any $\pi : \down \to \Set$, we have a subtopos inclusion
  $$\Set^{\down}_{\ulcorner/ \pi} \hookrightarrow \Set^{\down}_{/\pi}$$
  with lex localization given by vertical-cartesian factorization:
  \[
\begin{tikzcd}
E' \arrow[r] \arrow[d] & E \arrow[d, "\pi"] \\
B' \arrow[r]           & B                 
\end{tikzcd} \quad\quad\mapsto\quad\quad
\begin{tikzcd}
E' \arrow[d] \arrow[r, dashed]    & \bullet \arrow[d] \arrow[r] \arrow[rd, phantom, "\ulcorner" very near start] & E \arrow[d, "\pi"] \\
B' \arrow[r, equals] & B' \arrow[r]                           & B                 
\end{tikzcd}
  \]
  As a corollary, $\Dir_{\ulcorner/D} \hookrightarrow \Dir_{D}$ is a
  subtopos inclusion.
\end{thm}
\begin{proof}
We have displayed both the action of the left localization and its unit. The
counit is always an isomorphism since pullbacks are unique up to unique
isomorphism.

>>>>

We will show that $\Dir_{/_{\ulcorner} D}$ is a subtopos of $\Dir_{/D}$ with the
left exact left adjoint to the inclusion given by the vertical / cartesian factorization system on $\Set^{\down}$.

\begin{thm}
  For any $\pi : \down \to \Set$, we have a subtopos inclusion
  $$\Set^{\down}_{/_{\ulcorner} \pi} \hookrightarrow \Set^{\down}_{/\pi}$$

  with left exact left adjoint given by the vertical / cartesian factorization system:
  \[
\begin{tikzcd}
E' \arrow[r] \arrow[d] & E \arrow[d, "\pi"] \\
B' \arrow[r]           & B                 
\end{tikzcd} \quad\quad\mapsto\quad\quad
\begin{tikzcd}
E' \arrow[d] \arrow[r, dashed]    & \bullet \arrow[d] \arrow[r] \arrow[rd, phantom, "\ulcorner" very near start] & E \arrow[d, "\pi"] \\
B' \arrow[r, equals] & B' \arrow[r]                           & B                 
\end{tikzcd}
  \]
  As a corollary, $\Dir_{\ulcorner/D} \hookrightarrow \Dir_{D}$ is a
  subtopos inclusion.
\end{thm}
\begin{proof}
We have displayed both the action of the left localization and its unit. The
counit is always an isomorphism since pullbacks are unique up to unique
isomorphism.
